---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# delaunator

<!-- badges: start -->
<!-- badges: end -->

The goal of delaunator is to triangulate point sets fast. 

We have only wrapped this library for use in R: 
https://github.com/abellgithub/delaunator-cpp


WIP: An old benchmark to use for comparison: 

https://rpubs.com/cyclemumner/416456



## Installation

You can install the development version of delaunator like so:

``` r
#install.packages("remotes")
remotes::install_github("mdsumner/delaunator")
```

## Example



```{r example}
library(delaunator)
delaunator_triangulate(matrix(runif(6), ncol = 2))

delaunator_triangulate(cbind(1:4, runif(4)))

```


In the R level we sort out the orientation of inputs and outputs, and return a matrix of triangle triplets as rows (1-based). 

```{r orientation}
xy <- matrix(rnorm(1024), ncol = 2)
i <- delaunator_triangulate(xy)
plot(xy, asp = 1)
polygon(xy[t(cbind(i, NA)), ])

```


## No constrained triangulation here

If you're looking for constrained, conformant, or quality-of-mesh-controllable triangulation you won't find it here. These features are in RTriangle on CRAN, and there is some exposure of the CGAL library in R, and a functional version using RTriangle for some spatial data formats is in hypertidy/anglr. 

## Code of Conduct
  
Please note that the delaunator project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
